Data preparation

### 2019-12-12 data-prep.Rmd
Update data-prep.Rmd

dat99 <- cl99 %>% dplyr::select(v3,
                         v21,v16, # Salario percibio obrero y gerente
                         v31,v26, # Salario justo    obrero y gerente
                         v35,     # redistribucion
                         x_degr, # Educación 
                         v4:v8,v49:v55) # Meritocracia
#--- missing meritocracia -------------------------------------------------#
# Percepcion
dat99$v4 <- car::recode(dat99$v4,"c(8,9)=NA",as.numeric = TRUE)
dat99$v5 <- car::recode(dat99$v5,"c(8,9)=NA",as.numeric = TRUE)
dat99$v6 <- car::recode(dat99$v6,"c(8,9)=NA",as.numeric = TRUE)
dat99$v7 <- car::recode(dat99$v7,"c(8,9)=NA",as.numeric = TRUE)
dat99$v8 <- car::recode(dat99$v8,"c(8,9)=NA",as.numeric = TRUE)
dat99$v4 <- sjmisc::rec(dat99$v4,rec="rev")
dat99$v5 <- sjmisc::rec(dat99$v5,rec="rev")
dat99$v6 <- sjmisc::rec(dat99$v6,rec="rev")
dat99$v7 <- sjmisc::rec(dat99$v7,rec="rev")
dat99$v8 <- sjmisc::rec(dat99$v8,rec="rev")
# Preferencia
dat99$v49 <- car::recode(dat99$v49,"c(8,9)=NA",as.numeric = TRUE)
dat99$v50 <- car::recode(dat99$v50,"c(8,9)=NA",as.numeric = TRUE)
dat99$v51 <- car::recode(dat99$v51,"c(8,9)=NA",as.numeric = TRUE)
dat99$v52 <- car::recode(dat99$v52,"c(8,9)=NA",as.numeric = TRUE)
dat99$v53 <- car::recode(dat99$v53,"c(8,9)=NA",as.numeric = TRUE)
dat99$v54 <- car::recode(dat99$v54,"c(8,9)=NA",as.numeric = TRUE)
dat99$v55 <- car::recode(dat99$v55,"c(8,9)=NA",as.numeric = TRUE)
dat99$v49 <-sjmisc::rec(dat99$v49,rec="rev")
dat99$v50 <-sjmisc::rec(dat99$v50,rec="rev")
dat99$v51 <-sjmisc::rec(dat99$v51,rec="rev")
dat99$v52 <-sjmisc::rec(dat99$v52,rec="rev")
dat99$v53 <-sjmisc::rec(dat99$v53,rec="rev")
dat99$v54 <-sjmisc::rec(dat99$v54,rec="rev")
dat99$v55 <-sjmisc::rec(dat99$v55,rec="rev")
# Redistribucion
dat99$v35 <- car::recode(dat99$v35,"c(8,9)=NA",as.numeric = TRUE)
dat99$v35 <- sjmisc::rec(dat99$v35,rec="rev")
#Educacion
dat99$x_degr <- car::recode(dat99$x_degr, "c(9)=NA", as.numeric=TRUE)

@@

dat99 <- mutate(dat99, educ_rec = car::recode(dat99$educ, "3001:3004 = 1; 3005:3006 = 2;3008=2; 3010 = 3;3007 = 4; else = 3009"))             
table(dat99$educ_rec)

>>>>

dat99 <- cl99 %>% dplyr::select(v3,
                         v21,v16, # Salario percibio obrero y gerente
                         v31,v26, # Salario justo    obrero y gerente
                         v35,     # redistribucion
                         x_degr, # Educación 
                         v4:v8,v49:v55) # Meritocracia
#--- missing meritocracia -------------------------------------------------#
# Percepcion
dat99$v4 <- car::recode(dat99$v4,"c(8,9)=NA",as.numeric = TRUE)
dat99$v5 <- car::recode(dat99$v5,"c(8,9)=NA",as.numeric = TRUE)
dat99$v6 <- car::recode(dat99$v6,"c(8,9)=NA",as.numeric = TRUE)
dat99$v7 <- car::recode(dat99$v7,"c(8,9)=NA",as.numeric = TRUE)
dat99$v8 <- car::recode(dat99$v8,"c(8,9)=NA",as.numeric = TRUE)
dat99$v4 <- sjmisc::rec(dat99$v4,rec="rev")
dat99$v5 <- sjmisc::rec(dat99$v5,rec="rev")
dat99$v6 <- sjmisc::rec(dat99$v6,rec="rev")
dat99$v7 <- sjmisc::rec(dat99$v7,rec="rev")
dat99$v8 <- sjmisc::rec(dat99$v8,rec="rev")
# Preferencia
dat99$v49 <- car::recode(dat99$v49,"c(8,9)=NA",as.numeric = TRUE)
dat99$v50 <- car::recode(dat99$v50,"c(8,9)=NA",as.numeric = TRUE)
dat99$v51 <- car::recode(dat99$v51,"c(8,9)=NA",as.numeric = TRUE)
dat99$v52 <- car::recode(dat99$v52,"c(8,9)=NA",as.numeric = TRUE)
dat99$v53 <- car::recode(dat99$v53,"c(8,9)=NA",as.numeric = TRUE)
dat99$v54 <- car::recode(dat99$v54,"c(8,9)=NA",as.numeric = TRUE)
dat99$v55 <- car::recode(dat99$v55,"c(8,9)=NA",as.numeric = TRUE)
dat99$v49 <-sjmisc::rec(dat99$v49,rec="rev")
dat99$v50 <-sjmisc::rec(dat99$v50,rec="rev")
dat99$v51 <-sjmisc::rec(dat99$v51,rec="rev")
dat99$v52 <-sjmisc::rec(dat99$v52,rec="rev")
dat99$v53 <-sjmisc::rec(dat99$v53,rec="rev")
dat99$v54 <-sjmisc::rec(dat99$v54,rec="rev")
dat99$v55 <-sjmisc::rec(dat99$v55,rec="rev")
# Redistribucion
dat99$v35 <- car::recode(dat99$v35,"c(8,9)=NA",as.numeric = TRUE)
dat99$v35 <- sjmisc::rec(dat99$v35,rec="rev")
#Educacion
dat99$x_degr <- car::recode(dat99$x_degr, "c(3009)=NA", as.numeric=TRUE)

@@

dat99 <- mutate(dat99, educ_rec = car::recode(dat99$educ, "3001:3004 = 1; 3005:3006 = 2;3008=2; 3010 = 3;3007 = 4"))             
table(dat99$educ_rec)
